2024 US Election Prediction

### 2024-11-04 paper/paper.qmd

---
title: "2024 US Election Prediction"
subtitle: "An Analysis of Donald Trump’s Polling Trends and Predictive Outcomes"
author: 
  - Betty Liu
  - Jingchuan Xu
  - Dingshuo Li
thanks: "Code and data are available at: https://github.com/dawsonlll/2024_US_Election_Analysis"
date: Nov 04, 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
  html:
    toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "2024 US Election Prediction"
subtitle: "An Analysis of Donald Trump’s Polling Trends and Predictive Outcomes"
author: 
  - Betty Liu
  - Jingchuan Xu
  - Dingshuo Li
thanks: "Code and data are available at: https://github.com/dawsonlll/2024_US_Election_Analysis"
date: Nov 04, 2024
date-format: long
abstract: "The 2024 U.S. presidential election has sparked intense interest in the shifting dynamics of candidate support, particularly for Donald Trump. This paper examines polling data from multiple sources, employing linear and Bayesian models to analyze trends in Trump’s voter support over time. We find that while support fluctuates, it shows resilience across key demographics, revealing patterns that could significantly impact his electoral prospects. These insights contribute to our understanding of voter behavior in a polarized landscape, highlighting the factors that shape electoral outcomes."
format:
  pdf:
    toc: true
  html:
    toc: true
number-sections: true
bibliography: references.bib
---
